Hemodynamic responses of the Parahippocampal Place Area to spatial cues in a movie and its audio-description

### 2020-10-05 paper/main.tex
restructure discussion

\todo[inline]{Limit for Intro + Discussion (main text) = ca. 3k words;
intro is about 1k words (with to dos)}

@@

% brain mapping via fMRI
Cognitive neuroscientists use brain imaging methods like blood oxygenation
level-dependent functional magnetic resonance imaging (BOLD fMRI) to map
perceptual and cognitive brain processes (e.g. viewing of landscapes,
\citep{epstein1998ppa}; or theory of mind \citep{spunt2014validating}) to
functional brain areas or networks.
% What is the PPA?
A classic example of a functionally defined, higher-level visual area is the
``parahippocampal place area'' (PPA) \citep{epstein1998ppa,
epstein1999parahippocampal}.
% anatomical location != functional location
The PPA is located in the posterior parahippocampal gyrus including adjacent
regions of the fusiform gyrus \cite{epstein1998ppa} and anterior lingual gyrus
\citep{epstein2008parahippocampal}.
% neural correlate of scene perception
Increased hemodynamic activity in the PPA correlates with the perception of
static pictures of landscapes or landmarks compared to pictures of tools or
faces.
% spatial layout hypothesis
According to the spatial layout hypothesis, the PPA is involved in processing
the surface geometry of a visual stimulus and possibly in identifying scenes
based on their spatial layout \citep{epstein2010reliable}.
% literature review overview 1: imagination & haptic exploration
At a group average level, results generalize to mental imagination of landscapes
\citep{ocraven2000mental} and haptic exploration of scenes constructed from LEGO
blocks \citep{wolbers2011modality}.
% literature review overview 2: spoken sentences
One study that used spoken, place-related sentences showed significantly
decreased activation in the left and no modulation in the right-hemispheric PPA
\citep{aziz2008modulation}.

% literature review in detail
% O'Craven: Mental imagery
In the study conducted by \citep{ocraven2000mental} participants viewed
alternating blocks of pictures showing famous faces and familiar places during
an initial experimental paradigm. In a subsequent paradigm, participants were
instructed to ``form a vivid mental image'' of the previously viewed pictures.
The PPA showed increased activation during imagination of places compared to
faces but the imagination tasks showed a smaller activation level compared to
the perceptual task.

% Wolbers: haptic exploration
In the block design study conducted by \citep{wolbers2011modality} the PPA of
sighted participants showed increased activation during a delayed
matching-to-sample task of haptically explored scenes constructed from LEGO
bricks compared to haptically explored abstract geometric objects.
% connectivity analysis by Wolbers
\todo[inline]{Wolbers performed connectivity analysis between PPA and occipital
cortex, and compares connectivity during visual and haptic paradigm: ``The
scene-related increase in coupling with the PPA was significantly stronger in
multiple clusters in occipital cortex under visual than haptic stimulation
(Figure 2B; Table S2)''}
% Aziz (2008): place related sentences
\todo[inline]{lass uns kurz im Gespräch über Aziz Paper gucken; die relvanten
Abschnitte sind in der PDF markiert. Ihre Method Section ist ``strange'' und im
Grunde kommt überall nur uneinheitliche Grütze heraus; ich blicke nicht durch,
weshalb folgendes nicht vollständig korrekt sein wird;so wie ich es verstanden
habe, hat sie den Unterschied zwischen PPA und FFA angeguckt, aber diesen
Unterschied im Kontrast zu object-related Sentences (dortige Fig 3)}
% Aziz' stimuli
To our knowledge only one study \citep{aziz2008modulation} correlated
hemodynamic activity of the PPA with spoken sentences. Sentences described
generic or famous places (e.g. ``The Taj Mahal faces a long thin reflecting
pool''), faces  (``Marilyn Monroe has a large square jaw''), or objects (``The
television has a long antenna'').
% Aziz' tasks
Participants were instructed to press a button whenever the sentence described
an inaccurate or improbable fact.
% Aziz' results
Activation in the left, but not right, PPA was significantly reduced when
participants listened to place-related sentences compared to listening to
face-related sentences. Moreover, this effect was only observed in sentences
involving famous places.

@@

% summary if literature review
In summary, studies suggest that the PPA does preferably but not exclusively
respond to visually presented spatial information.
% shortcomings of previous studies: simplified stimuli
Nevertheless, all reviewed studies have in common that they employed a small set
of simplified stimuli to strictly control experimental conditions.
% shortcomings of previous studies: task-based paradigm
Further, they usually relied on explicit judgment-based tasks to ensure that
participants payed attention to the stimuli.
% disadvantage 1b: lack of validity
Paradigms using block designs accompanied with a task have the disadvantage that
they do not resemble our real-life experience and thus lack external validity
\citep{westfall2016fixing} as well as ecological validity
\citep{hasson2004intersubject}.
% disadvantage 2a: averaging for group results
Additionally, the reviewed studies averaged results across 7-11 subjects to
improve the signal-to-noise-ratio (SNR).
% disadvantage 2b: no individual level
The disadvantage here is that the averaging approach does not characterize brain
functions at an individual level, a prerequisite for the application of brain
imaging methods in individual diagnostics (cf. \citep{dubois2016building,
eickhoff2020towards}).
% open questions
This raises the question how the PPA behaves under life-like conditions, and how
group results a driven by individuals subjects especially in response to
audio-only stimulation\todo{``audio-only'' sounds meh; ``exclusively auditory
stimulation''?}.
% Huth (2016)
\todo[inline]{Huth et al. (2016) implicitly regarding audio-only; but they do
not discuss the PPA; in general, they do voxel-wise encoding which doesn't say
anything about excitation/inhibition}

% naturalistic stimuli
Paradigms using naturalistic stimuli like movies
\citep{hasson2008neurocinematics, sonkusare2019naturalistic} or narratives
\citep{honey2012not, lerner2011topographic, silbert2014coupled} offer complex,
continuous stimulation that better resemble our experience of a our dynamic
environment.
% naturalistic stimuli review: intro
Two early studies using naturalistic stimuli suggest functional specialization
of brain areas is preserved during movie watching when many perceptual and
cognitive processes are triggered simultaneously \citep{bartels2004mapping,
hasson2004intersubject}.
% Bartels (2004): Film + GLM (but surprisingly did not annotate landscapes)
\citep{bartels2004mapping} manually annotated time points that depict faces and
human bodies in a 22 minute clip of the movie \textit{Tomorrow Never Dies}
\citep{tomorrowneverdies}.
% Bartels: results
Employing a general linear model (GLM) to model hemodynamic activity, these time
points correlated with increased activity in the ``fusiform face area''
\citep{kanwisher1997ffa} and ``extrastriate body area''
\citep{downing2001bodyarea} respectively.
% Hasson (2004): Film + (reverse) ISC
Employing a reverse intersubject correlation, \citep{hasson2004intersubject}
used a 30 minute clip of the movie \textit{The Good, the Bad, and the Ugly}
\citep{goodbadugly}.
% Hasson: method
fMRI brain volumes showing the highest hemodynamic activity in the PPA [across
(five) participants] were matched to the temporally corresponding movie frames.
% Hasson: results
Results revealed that corresponding movie frames depicted indoor and outdoor
scenes including buildings and open fields.
% summary naturalistic stimuli
Nevertheless, both studies used an audio-visual stimulus and again do not
address the question how the investigated functional areas respond an audio-only
stimulus.

@@

% what we did: data source
In the current study, we analyze publicly available functional data
(studyforrest.org) of the same 14 participants watching a movie
\citep{hanke2016simultaneous} and listening to an audiobook.
\citep{hanke2014audiomovie}.
% PPA + movie + audio-description
We annotated cuts in the movie ``Forrest Gump'' \citep{ForrestGumpMovie}, and
words spoken by an additional narrator in the movie's audio-description (i.e.
the movie's audio-only variant; \citep{ForrestGumpGermanAD}) to exploratorily
investigate how the parahippocampal gyrus behaves during more life-like
conditions free from any task.
% traditional GLM
We do this by analyzing our data by constructing GLM contrasts as canonically
used to analyze data from tightly controlled paradigms.
% focus on audio-description
Encouraged by \citep{aziz2008modulation}, we focus on the audio-description as
an audio-only paradigm and test its localization performance of a ``visual
area'' in individual study participants.
% comparison to dedicated localizer
Finally, we compare these results to results of a dedicated visual localizer
experiment done with the same participants \citep{sengupta2016extension}.

\todo[inline]{maybe insert ``foreshadowing'' of results here?}
\todo[inline]{Bzgl. Open Source der Ergebnisse/Skripte: Dazu habe ich hier nichts geschrieben, weil ich nur weiß, das der Code veröffentlicht werden soll. Du hast die Vision diesbezüglich im Kopf und entsprechend auch kanonisch-prägnante Formulierungen und wo die am besten wie hinkommen}

@@

\todo[inline]{Specific data outputs should be explicitly referenced via data
citation (see Data Records and Data Citations, below)}
\todo[inline]{explain as introduction to every step why it woes done}
\todo[inline]{current order of subsections might be ``non-canonical''}
\todo[inline]{parts from original studies might still be too detailed}

% intro
We used data from three publicly available datasets
(\href{http://www.studyforrest.org}{studyforrest.org}) that have already been
used by other research groups for independent research questions.
% used studies
The same subjects were
% AO
a) listening to the audio-description (AO study; \citep{hanke2014audiomovie}) of
the movie ``Forrest Gump'', a dataset already used by \citep{hu2017decoding,
nguyen2016integration},\todo{this is kind of a loveless list}
% AV
b) watching the actual audio-visual movie (AV study;
\citep{hanke2016simultaneous}), a dataset already used by
\citep{ben2018hippocampal},
% VIS
c) participating in a dedicated six-category block-design visual localizer (VIS
study; \citep{sengupta2016extension}), a dataset already used by
\citep{jiahui2019predicting}.
% see corresponding papers for details
An exhaustive description of the participants, stimulus creation, procedure,
stimulation setup, and fMRI acquisition can be found in the corresponding
publications. Following is a summary of most important aspects.

\subsection{Participants}
% AO study
In the AO study \citep{hanke2014audiomovie}, 20 German native speakers (all
right-handed, age 21–38 years, mean age 26.6 years, 12 male) listened to the
German audio-description \citep{ForrestGumpGermanAD} of the movie ``Forrest
Gump'' \citep{ForrestGumpMovie} as an additional audio track for visually
impaired listeners on Swiss public television.
% AV study
In the AV study \citep{hanke2016simultaneous}, 15 participants (21–39 years,
mean age 29.4, six female) of the prior AO study watched the audio-visual movie
with dubbed German audio track \citep{ForrestGumpDVD}.
% VIS study
In the VIS study \citep{sengupta2016extension}, the same 15 participants took
part in a six-category block-design visual localizer.

@@

\subsection{Stimuli}
% AO & AV stimulus name & references
We used the German DVD release \citep{ForrestGumpDVD} of the audio-visual movie
``Forrest Gump'' \citep{ForrestGumpMovie} and its temporally aligned
audio-description that was broadcast as an additional audio track for visually
impaired listeners on Swiss public television \citep{ForrestGumpGermanAD}.
% AV: voice-over
The plot of the movie is already carried by a voice-over of the main character
Forrest Gump.
% AO: additional narrator
In the largely identical audio-description, an additional male narrator
describes essential aspects of the visual scenery when there is no off-screen
voice, dialog, or other relevant auditory content.

% AO & AV: stimulus creation
The audio-description was temporally aligned to the audio track of the German
DVD release. A few scenes less relevant to the major plot were removed to create
the ``research cut'' lasting $\approx$ \unit[2]{h} \citep{hanke2014audiomovie,
hanke2016simultaneous}.
% further processing
Both stimuli were further processed (filtering, volume adjustments) to improve
audibility during MRI scanning. Black horizontal bars at the top and bottom of
the movie were replaced with medium-gray bars of the same size in order to
increase background illumination for a more pleasant experience.
% splitting
Each stimulus was split into eight segments of approximately 15 minutes. Except
for the first movie segment, each segment started with a snippet of at least six
seconds immediately preceding the movie scene boundary used to split the
segments (see Figure 3a in \citep{hanke2014audiomovie}).

@@

\subsection{Naturalistic stimuli annotation}
%todo
% stimuli were not designed for research purposes
Both natural stimuli were originally designed to entertain an audience and to
capture attention free from any perceptual or behavioral task.
% AO annotation
For the analysis of the AO data, we extended an publicly available annotation of
speech \citep{haeusler2020speechanno} by further annotating words spoken by the
audio-description's narrator.
% annotation procedure
Two persons performed a categorization of nouns that the narrator uses to
describe the movie's missing visual content.
% why and how of categories 1
Some categories were created in such a way to reflect the six stimulus
categories used in the visual localizer experiment.
% why and how of categories 2
Some additional categories were created to semantically cluster nouns into
categories ``that were obvious to make sense''.\todo{yeah, well, sounds shit but
that's basically it}
% categories in detail
Nouns were categorized by the verbal clue they provide about the cinematographic
scene's environment (\texttt{geo}, \texttt{geo-room}; \texttt{setting\_new},
\texttt{setting\_old}), its inherent persons (e.g. \texttt{female},
\texttt{male}, \texttt{persons}), a person's body or worn clothes
(\texttt{face}, \texttt{head}, \texttt{body}, \texttt{bodypart}), and a scene's
inherent objects (\texttt{object}, \texttt{furniture}).
% problem with hierarchical categories
\todo[inline]{put stuff regarding hierarchical categories and heterogeneity
here; counts in table show the counts of just the primary category; settings
changes often (30-60 \%) belong to another category; most often it's geo but
also object or male/mname/furniture; cf. Results and Discussion regarding
stability of contrasts}
% reference to table with rules and examples
A complete overview of all 19 categories, the rule for a word to belong to a
category, and examples can be seen in \ref{tab:descr-nouns-rules}.
% procedure
A preliminary annotation was performed by one person according to the rules.
Minor corrections due to incorrectly applied rules were done by the author.
% reference to table with counts
The resulting counts for the whole stimulus and the eight stimulus segments used
during fMRI scanning can be seen in Table \ref{tab:descr-nouns-counts}.

% AV anno
For the analysis of the AV data, we took advantage of a publicly available
annotation of movie cuts and depicted locations \citep{haeusler2016cutanno}.
In/for the movie, We annotated different kinds of cinematographic cuts
\citep{haeusler2016cutanno} as presumably ``spatially relevant'' events.
% rationale behind using movie cuts
Our rationale was that cuts are ``spatially relevant'' events that re-orient the
viewer in the depicted environment independent from the exact visual content in
the movie frame following the cut.

@@

% table for descriptive nouns: categories, rules, examples counts
\begin{table*}[t]
    \caption{Descriptive nouns spoken by the audio-description's narrator:
    categories, annotation rules, and examples (given in English). The category
    \texttt{++} also contains adverbial of time.}
\label{tab:descr-nouns-rules}
\begin{tabular}{lll}
\toprule
\textbf{category} & \textbf{rule} & \textbf{examples} \\
\midrule
body & trunk of the body; overlaid clothes & back, hip, shoulder; jacket, dress, shirt \tabularnewline
bodypart & limbs and trousers & arm, finger, leg, toe \tabularnewline
face & face or parts of it & face, ear, nose, mouth \tabularnewline
female & female person & nurse, mother, woman \tabularnewline
females & female persons & women \tabularnewline
fname & female name & Jenny \tabularnewline
furniture & movable furniture insides \& outsides & bench, bed, table, chair
\tabularnewline
geo & immobile landmarks & building, tree, street, alley, meadow, cornfield \tabularnewline
geo-room & rooms (insides) or  locales (outsides) & living room; wall, door, window, floor, turf \tabularnewline
head & non-face parts of the head; worn headgear & head, hair, ear, neck,
helmet \tabularnewline
male & male person & man, father, soldier \tabularnewline
males & male persons & boys, opponents \tabularnewline
mname & male name & Bubba, Kennedy \tabularnewline
object & countable entity with firm boundaries & telephone, car \tabularnewline
objects & countable entities & wheels, plants \tabularnewline
persons & concrete persons of unknown sex & hippies, patients \tabularnewline
setting\_new & noun cueing a new setting &  on a ``bridge'', on an ``alley'', on ``campus'' \tabularnewline
setting\_rec & noun cueing a recurring setting & at the ``bus stop'' \tabularnewline
++ & cue regarding time & in the ``evening'', it's ``daytime'', ``later'' \tabularnewline

@@

\subsection{Procedure}
% questionnaire
In all three studies, participants filled out a questionnaire on their basic
demographic information and familiarity with the movie.
% AO & AV: instructions
Participants were instructed to inhibit physical movements except for
eye-movements, and otherwise to simply ``enjoy the audiobook'' or ``enjoy the
movie'' respectively.
% AO & AV: presentation & instructions
Audio-description and movie segments were presented in chronological order with
four segments in two fMRI sessions. Between sessions, participants left the
scanner for a break with a flexible duration. Structural images were obtained
during the first study on a day different from the fMRI session.

@@

% AO
In the AO study, visual instructions were presented on a rear-projection screen
inside scanner bore using an LCD projector (DLA-G150CL, JVC Ltd.). During the
functional scans, the projector presented a medium gray screen with the primary
purpose to illuminate a participant's visual field in order to prevent premature
fatigue. [The screen contained a solid black ``fixation'' dot that faded in and
out at the beginning and end of a movie segment.]

% AV & VIS
In the AV and VIS study, visual instructions and stimuli were presented on a
rear-projection screen using an LCD projector (JVC DLA RS66E, JVC Ltd., light
transmission reduced to \unit[13.7]{\%} with a gray filter) connected to the
stimulus computer [via a DVI extender system (Gefen EXT-DVI-142DLN with
EXT-DVI-FM1000)].
% screen size
The movie was shown at a viewing distance of \unit[63]{cm} in \unit[720]{p}
resolution at full width on a \unit[1280 $\times$ 1024]{pixel} screen with
\unit[60]{Hz} video refresh rate and screen dimension of \unit[26.5 $\times$
21.2]{cm}.
% angle of view: AV
In the AV study, this corresponded to \unit[23.75 $\times$ 13.5] or \unit[23.75
$\times$ 10.25]{cm} when considering only the movie content and excluding the
horizontal gray bars.
% angle of view: VIS
In the VIS study, stimulus images were displayed at a size of approximately
\unit[10]$^{\circ}$ $\times$ \unit[10]$^{\circ}$ of visual angle.

@@

\todo[inline]{Why done this way? Why is no. 1 the one? Event count,
se\_new and se\_old only vaguely describe the scene; narrator is often
lacking behind dialogue and change in soundscape}

>>>>

\todo[inline]{Limit for main text (intro and discussion) = ca. 3k words;
intro is about 1k words (with to dos)}

@@

% brain mapping via fMRI
Cognitive neuroscientists use brain imaging methods like blood oxygenation
level-dependent functional magnetic resonance imaging (BOLD fMRI) to map
perceptual and cognitive brain processes (e.g. viewing of faces
\citep{kanwisher1997ffa} or theory of mind \citep{spunt2014validating}) to
functional brain areas or networks.
% What is the PPA?
A classic example of a functionally defined, higher-level visual area is the
``parahippocampal place area'' (PPA) \citep{epstein1998ppa,
epstein1999parahippocampal}.
% anatomical location != functional location
The PPA is located in the posterior parahippocampal gyrus including adjacent
regions of the fusiform gyrus and anterior lingual gyrus
\citep{ epstein2008parahippocampal}.
% neural correlate of scene perception
Increased hemodynamic activity in the PPA correlates with the perception of
static pictures of landscapes, buildings or landmarks \citep{aguirre1998area, epstein2014neural, epstein1998ppa} compared to e.g. pictures of tools of faces.
% spatial layout hypothesis
[[According to the spatial layout hypothesis, the PPA is involved in processing
the surface geometry of a visual stimulus and possibly in identifying scenes
based on their spatial layout \citep{epstein2010reliable}.]]\todo{better delete}
% literature review overview 1: imagination & haptic exploration
At a group average level, results generalize to mental imagination of landscapes
\citep{ocraven2000mental} and haptic exploration of scenes constructed from LEGO
blocks \citep{wolbers2011modality}.
% literature review overview 2: spoken sentences
One study that used spoken, place-related sentences showed significantly
decreased activation in the left and no modulation in the right-hemispheric PPA
\citep{aziz2008modulation}.

% literature review in detail
% O'Craven: Mental imagery
In the study conducted by \cite{ocraven2000mental} participants viewed
alternating blocks of pictures showing famous faces and familiar places during
an initial experimental paradigm. In a subsequent paradigm, participants were
instructed to ``form a vivid mental image'' of the previously viewed pictures.
The PPA showed increased activation during imagination of places compared to
faces but the imagination tasks showed a smaller activation level compared to
the perceptual task.

% Wolbers: haptic exploration
In the block design study conducted by \cite{wolbers2011modality} the PPA of
sighted participants showed increased activation during a delayed
matching-to-sample task of haptically explored scenes constructed from LEGO
bricks compared to haptically explored abstract geometric objects.
% connectivity analysis by Wolbers
\todo[inline]{Wolbers performed connectivity analysis between PPA and occipital
cortex, and compares connectivity during visual and haptic paradigm: ``The
scene-related increase in coupling with the PPA was significantly stronger in
multiple clusters in occipital cortex under visual than haptic stimulation
(Figure 2B; Table S2)''}

\todo[inline]{following phrasing might be strange but necessary to delineate
from Huth (2016); good voxel-wise semantic modeling regarding places in PPA but
imo that does not say anything about excitation/inhibition; interestingly Huth
mentions PPA during talks but it is not discussed in any paper and despite being
promised none of his group came up with a paper regarding that topic}
% Aziz (2008): place related sentences
To our knowledge only one study \citep{aziz2008modulation} investigated how
hemodynamic activity in the PPA differs between stimulus features of spoken
language.
% Aziz' stimuli
\cite{aziz2008modulation} used sentences that described generic or famous places
(e.g. ``The Taj Mahal faces a long thin reflecting pool''), faces  (``Marilyn
Monroe has a large square jaw''), or objects (``The television has a long
antenna'').
% Aziz' tasks
Participants were instructed to press a button whenever the sentence described
an inaccurate or improbable fact.
% Aziz' results
Activation in the left, but not right, PPA was significantly reduced when
participants listened to place-related sentences compared to listening to
face-related sentences. Moreover, this effect was only observed in sentences
involving famous places.
% wtf did Aziz really do?
\todo[inline]{lass uns bitte kurz im Gespräch über Aziz Paper gucken; die
relvanten Abschnitte sind in der PDF markiert. Ihre Method Section ist
``strange'' und im Grunde kommt überall nur uneinheitliche Grütze heraus; ich
blicke nicht durch, weshalb geschriebenes nicht vollständig korrekt sein wird;
so wie ich es verstanden habe, hat sie vier 2x2 ANOVAs den Unterschied zwischen
PPA und FFA angeguckt, aber diesen Unterschied im Kontrast zu object-related
Sentences (dortige Fig 3)}

@@

% summary if literature review
In summary, studies suggest that the PPA does preferably but not exclusively
respond to visually presented spatial information.
% shortcomings of previous studies: simplified stimuli
Nevertheless, all reviewed studies have in common that they employed a small set
of simplified stimuli to strictly control experimental conditions.
% shortcomings of previous studies: task-based paradigm
Further, they usually relied on explicit judgment-based tasks to ensure that
participants payed attention to the stimuli.
% disadvantage 1b: lack of validity
Paradigms using block designs accompanied with a task have the disadvantage that
they do not resemble our real-life experience and thus lack external validity
\citep{westfall2016fixing} as well as ecological validity
\citep{hasson2004intersubject}.
% disadvantage 2a: averaging for group results
Additionally, the reviewed studies averaged results across 7-11 subjects to
improve the signal-to-noise-ratio (SNR).
% disadvantage 2b: no individual level
The disadvantage here is that the averaging approach does not characterize brain
functions at an individual level, a prerequisite for the application of brain
imaging methods in individual diagnostics (cf. \cite{dubois2016building,
eickhoff2020towards}).
% open questions
This raises the question how the PPA behaves under life-like conditions, and how
group results a driven by individuals subjects especially in response to
audio-only stimulation\todo{``audio-only'' sounds meh?}.

% naturalistic stimuli
Paradigms using naturalistic stimuli like movies
\citep{hasson2008neurocinematics, sonkusare2019naturalistic} or narratives
\citep{honey2012not, lerner2011topographic, silbert2014coupled} offer complex,
continuous stimulation that better resemble the experience of our dynamic
environment.
% naturalistic stimuli review: intro
Two early studies using naturalistic stimuli suggest functional specialization
of brain areas is preserved during movie watching when many perceptual and
cognitive processes are triggered simultaneously \citep{bartels2004mapping,
hasson2004intersubject}.
% Bartels (2004): Film + GLM (but surprisingly did not annotate landscapes)
\cite{bartels2004mapping} manually annotated time points that depict faces and
human bodies in a 22 minute clip of the movie \textit{Tomorrow Never Dies}
\citep{tomorrowneverdies}.
% Bartels: results
Employing a general linear model (GLM) to model hemodynamic activity, these time
points correlated with increased activity in the ``fusiform face area''
\citep{kanwisher1997ffa} and ``extrastriate body area''
\citep{downing2001bodyarea} respectively.
% Hasson (2004): Film + (reverse) ISC
Employing a reverse intersubject correlation, \cite{hasson2004intersubject} used
a 30 minute clip of the movie \textit{The Good, the Bad, and the Ugly}
\citep{goodbadugly}.
% Hasson: method
fMRI brain volumes showing the highest hemodynamic activity in the PPA [across
(five) participants] were matched to the temporally corresponding movie frames.
% Hasson: results
Results revealed that corresponding movie frames depicted indoor and outdoor
scenes including buildings and open fields.
% summary naturalistic stimuli
Nevertheless, both studies used an audio-visual stimulus and again do not
address the question how the investigated functional areas respond during an
audio-only stimulus.

@@

% what we did: data source
In the current study, we analyze publicly available functional data
(studyforrest.org) of the same 14 participants watching a movie
\citep{hanke2016simultaneous} and listening to an audiobook.
\citep{hanke2014audiomovie}.
% PPA + movie + audio-description
We annotated cuts in the movie ``Forrest Gump'' \citep{ForrestGumpMovie}, and
words spoken by an additional narrator in the movie's audio-description (i.e.
the movie's audio-only variant; \citep{ForrestGumpGermanAD}) to exploratorily
investigate how the parahippocampal gyrus behaves during more life-like
conditions free from any task.
% traditional GLM
We do this by analyzing our data by constructing GLM contrasts as canonically
used to analyze data from tightly controlled paradigms.
% focus on audio-description
Encouraged by \citep{aziz2008modulation}, we focus on the audio-description as
an audio-only paradigm. We further test the audio-description's localization
performance of a ``visual area'' in individual study participants by comparing
our results to results of a dedicated visual localizer experiment done with the
same participants \citep{sengupta2016extension}.
% results
Our results demonstrate that (a), (b), (c)... \todo{similar to abstract and
conclusion}

\todo[inline]{Bzgl. Open Source der Ergebnisse/Skripte: Dazu habe ich hier
nichts geschrieben; probably something like ``all raw data, scripts, and
results are available under xy as datalad/BIDS dataset''}

@@

\todo[inline]{Specific data outputs should be explicitly referenced via data
citation (see Data Records and Data Citations, below)}
\todo[inline]{current order of subsections might be ``non-canonical''}
\todo[inline]{parts from original studies probably too detailed}

% intro
We used data from three publicly available datasets
(\href{http://www.studyforrest.org}{studyforrest.org}) that have already been
used by other research groups for independent research questions.
% used studies
The same subjects were
% AO
a) listening to the audio-description (AO study; \citep{hanke2014audiomovie}) of
the movie ``Forrest Gump'', a dataset already used by \citep{hu2017decoding,
nguyen2016integration},\todo{this is kind of a loveless list}
% AV
b) watching the actual audio-visual movie (AV study;
\citep{hanke2016simultaneous}), a dataset already used by
\citep{ben2018hippocampal},
% VIS
c) participating in a dedicated six-category block-design visual localizer (VIS
study; \citep{sengupta2016extension}), a dataset already used by
\citep{jiahui2019predicting}.
% see corresponding papers for details
An exhaustive description of the participants, stimulus creation, procedure,
stimulation setup, and fMRI acquisition can be found in the corresponding
publications. Following is a summary of the most important aspects.

\subsection{Participants}
% AO study
In the AO study \citep{hanke2014audiomovie}, 20 German native speakers (all
right-handed, age 21–38 years, mean age 26.6 years, 12 male) listened to the
German audio-description \citep{ForrestGumpGermanAD} of the movie ``Forrest
Gump'' \citep{ForrestGumpMovie}.
% AV study
In the AV study \citep{hanke2016simultaneous}, 15 participants (21–39 years,
mean age 29.4, six female) of the prior AO study watched the audio-visual movie
with dubbed German audio track \citep{ForrestGumpDVD}.
% VIS study
In the VIS study \citep{sengupta2016extension}, the same 15 participants took
part in a six-category block-design visual localizer.

@@

\subsection{Stimuli}
% AO & AV stimulus name & references
We used the German DVD release \citep{ForrestGumpDVD} of the audio-visual movie
``Forrest Gump'' \citep{ForrestGumpMovie} and its audio-description that was
broadcast as an additional audio track for visually impaired listeners on Swiss
public television \citep{ForrestGumpGermanAD}.
% AV: voice-over
The plot of the movie is already carried by a voice-over of the main character
Forrest Gump.
% AO: additional narrator
In the largely identical audio-description, an additional male narrator
describes essential aspects of the visual scenery when there is no off-screen
voice, dialog, or other relevant auditory content.

% AO & AV: stimulus creation
The audio-description was temporally aligned to the audio track of the German
DVD release. A few scenes less relevant to the major plot were removed to create
the ``research cut'' lasting $\approx$ \unit[2]{h} \citep{hanke2014audiomovie,
hanke2016simultaneous}.
% further processing
Both stimuli were further processed (filtering, volume adjustments) to improve
audibility during MRI scanning. Black horizontal bars at the top and bottom of
the movie were replaced with medium-gray bars of the same size in order to
increase background illumination for a more pleasant experience.
% splitting
Each stimulus was split into eight segments of approximately 15 minutes. Except
for the first segment, each segment started with a snippet of at least six
seconds immediately preceding the movie scene boundary used to split the
segments (see Figure 3a in \citep{hanke2014audiomovie}).

@@

\subsection{Naturalistic stimuli annotation}
% todo stimuli were not designed for research purposes
Both natural stimuli were originally designed to entertain their audiences and
to capture attention free from any perceptual or behavioral task.
% AO annotation
Thus for the analysis of the AO data, we extended an publicly available
annotation of speech \citep{haeusler2020speechanno} by further annotating words
spoken by the audio-description's narrator.
% annotation procedure
Two persons performed a categorization of nouns that the narrator uses to
describe the movie's missing visual content.
% categories in detail
Nouns were categorized by the verbal clue they provide about the cinematographic
scene's environment (\texttt{geo}, \texttt{geo-room}; \texttt{setting\_new},
\texttt{setting\_old}), its inherent persons (e.g. \texttt{female},
\texttt{male}, \texttt{persons}), a person's body or worn clothes
(\texttt{face}, \texttt{head}, \texttt{body}, \texttt{bodypart}), and a scene's
inherent objects (\texttt{object}, \texttt{furniture}).
% why and how of categories 1
Some categories were created to reflect the six stimulus categories used in the
visual localizer experiment (e.g. \texttt{geo}, \texttt{object}).
% why and how of categories 2
Other categories were created to semantically cluster some remaining nouns into
additional categories (e.g. \texttt{fname}, \texttt{furniture})
% problem with hierarchical categories
Notably, the categories \texttt{setting\_new} and \texttt{setting\_rec}
comprise not just words that describe an abstract location (e.g. ``in
Greenbow'') or a setting as whole (e.g. ``the platoon wades through a rice
field'', ``in a disco''). They also comprise words that could count as a member
of another categories in case the narrator uses these words to indicate a switch
from one setting to another (e.g. ``near an old bus'').
% reference to table with rules and examples
A complete overview of all 19 categories, the rule for a word to belong to a
category, and examples can be seen in Table \ref{tab:descr-nouns-rules}.
% procedure
A preliminary annotation was performed by one person according to the rules.
Minor corrections due to incorrectly applied rules were done by the author.
% reference to table with counts
The resulting counts for the whole stimulus and the eight stimulus segments used
during fMRI scanning can be seen in Table \ref{tab:descr-nouns-counts}.

% AV anno
For the analysis of the AV data, we took advantage of a publicly available
annotation of movie cuts and depicted locations \citep{haeusler2016cutanno}.
% rationale behind using movie cuts
Our rationale was that cuts are ``spatially relevant'' events that re-orient the
viewer within the environment depicted in the movie.

@@

% table for descriptive nouns: categories, rules, examples counts
\begin{table*}[t]
    \caption{Descriptive nouns spoken by the audio-description's narrator:
    categories, annotation rules, and examples (given in English). The category
    \texttt{++} also contains adverbial of time.}
\label{tab:descr-nouns-rules}
\begin{tabular}{lll}
\toprule
\textbf{category} & \textbf{rule} & \textbf{examples} \\
\midrule
body & trunk of the body; overlaid clothes & back, hip, shoulder; jacket, dress, shirt \tabularnewline
bodypart & limbs and trousers & arm, finger, leg, toe \tabularnewline
face & face or parts of it & face, ear, nose, mouth \tabularnewline
female & female person & nurse, mother, woman \tabularnewline
females & female persons & women \tabularnewline
fname & female name & Jenny \tabularnewline
furniture & movable furniture insides \& outsides & bench, bed, table, chair
\tabularnewline
geo & immobile landmarks & building, tree, street, alley, meadow, cornfield \tabularnewline
geo-room & rooms (insides) or  locales (outsides) & living room; wall, door, window, floor, turf \tabularnewline
head & non-face parts of the head; worn headgear & head, hair, ear, neck,
helmet \tabularnewline
male & male person & man, father, soldier \tabularnewline
males & male persons & boys, opponents \tabularnewline
mname & male name & Bubba, Kennedy \tabularnewline
object & countable entity with firm boundaries & telephone, car \tabularnewline
objects & countable entities & wheels, plants \tabularnewline
persons & concrete persons of unknown sex & hippies, patients \tabularnewline
setting\_new & noun cueing an unfamiliar setting &  on a ``bridge'', on an ``alley'', on ``campus'' \tabularnewline
setting\_rec & noun cueing a recurring setting & at the ``bus stop'' \tabularnewline
++ & cue regarding time & in the ``evening'', it's ``daytime'', ``later'' \tabularnewline

@@

\subsection{Procedure}
% questionnaire
Participants filled out a questionnaire on their basic demographic information
and familiarity with the movie.
% AO & AV: instructions
Participants were instructed to inhibit physical movements except for
eye-movements, and otherwise to simply ``enjoy the audiobook'' or ``enjoy the
movie'' respectively.
% AO & AV: presentation & instructions
Audio-description and movie segments were presented in chronological order with
four segments in two fMRI sessions. Between sessions, participants left the
scanner for a break with a flexible duration. Structural images were obtained
during the first study on a day different from the fMRI session.

@@

% AO
In the AO study, visual instructions were presented on a rear-projection screen
inside scanner bore using an LCD projector (DLA-G150CL, JVC Ltd.). During the
functional scans, the projector presented a medium gray screen with the primary
purpose to illuminate a participant's visual field in order to prevent premature
fatigue.

% AV & VIS
In the AV and VIS study, visual instructions and stimuli were presented on a
rear-projection screen using an LCD projector (JVC DLA RS66E, JVC Ltd., light
transmission reduced to \unit[13.7]{\%} with a gray filter) connected to the
stimulus computer.
% screen size
The movie was shown at a viewing distance of \unit[63]{cm} in \unit[720]{p}
resolution at full width on a \unit[1280 $\times$ 1024]{pixel} screen with
\unit[60]{Hz} video refresh rate and screen dimension of \unit[26.5 $\times$
21.2]{cm}.
% angle of view: AV
In the AV study, this corresponded to \unit[23.75 $\times$ 13.5] or \unit[23.75
$\times$ 10.25]{cm} when considering only the movie content and excluding the
horizontal gray bars.
% angle of view: VIS
In the VIS study, stimulus images were displayed at a size of approximately
\unit[10]$^{\circ}$ $\times$ \unit[10]$^{\circ}$ of visual angle.

@@

\todo[inline]{send me to hell for the following paragraphs but it is detailed at
least}
